Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-14 manuscript/manuscript.tex
Added figure spherical-shell

Lets consider a spherical shell with inner and outer radii $R_1$ and $R_2$, respectivetly, which density depends on the radius spherical coordinate.
The gravity potential generated by the shell on an arbitrary external point $Q(0,0,r)$ located along the $z$ axis at a distance $r$ can be written as follows:

\todo{figura spherical shell con punto Q}

>>>>

Lets consider a spherical shell with inner and outer radii $R_1$ and $R_2$, respectivetly, which density depends on the radius spherical coordinate.
The gravity potential generated by the shell on an arbitrary external point $Q(0,0,r)$ located along the $z$ axe at a distance $r$ can be written as follows:

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/spherical-shell.pdf}
\caption{
Spherical shell with inner and outer radii $R_1$ and $R_2$, respectively.
The computation point $Q$ is located in the $z$ axe at a distance $r$ from the centre of the shell.
For practical purposes we will assume that $Q$ is outside the outer radii, i.e. $r > R_2$.
}
\label{fig:spherical-shell}
\end{figure}
